---
title: "Online News Popularity - Analysis Report"
author: Nagraj Rao, Linhan Cai, Jennifer Hoang
date: "`r Sys.Date()`"
bibliography: "online_news_pop.bib"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary



## Introduction

The online news market space has grown rapidly in recent decades, leading to increased competition between traditional news outlets and non-traditional digital news sources. Understanding the factors associated with popularity of news articles online is vital for guiding publishing strategies of news agencies in order for them to remain competitive in the online news space. Here, we assessed factors associated with online news popularity using a public dataset with statistics from originally published on Mashable (www.mashable.com) in 2015 [@online-news].


## Methods

### Data Cleaning



### Statistical Analysis
#### EDA
During EDA on the raw data, we try merging data channels and the weekday columns into one column, then explore data type of the variables in the data set and summary Statistics for each variable. By creating correlation plot and correlation matrix, we try to find out the important features and in the end, we explore bar graph showing how number of shares vary based on topic, how number of shares vary based on day of the week, and try histogram showing how number of shares vary based on day of the week.  The code used to perform the EDA can be found [here](https://github.com/UBC-MDS/online_news_popularity/tree/main/src).



## Results
#### EDA
Through exploratory data analysis, we determined that some of the features were not informative to answering our question or contained many missing values.

(NEED CHANGES??????Before model testing, data cleaning was done to address the findings of  non-informative features, class imbalance, NAN values, and duplicate encounters, and this code can be found [here](https://github.com/UBC-MDS/group29/blob/main/src/processingdata.py). Non informative features included encounter id and patient number as those were entirely unique values. We removed weight, payer_code, medical_speciality, examide and citoglipton because much of the information was missing or all values in the column were the same. We were unsure about the race columns as majority of the patients were Caucasian and we did not want to add any racial biases to the data. As shown below, the distribution of race was reviewed to determine that there was no significant difference between different races in patient readmission and therefore the race column was removed from our analysis to prevent any bias.

```{r race_figure, echo=FALSE, fig.cap="Figure 1. Distribution of Race and Readmission Status", out.width = '40%', fig.align = 'center'}
knitr::include_graphics("../reports/figures/figure1_racedist_eda.svg")
```

Several of the numerical features were reviewed by plotting the distribution of the feature for the two different target classes against each other and found the primary diagnosis of the patient, days spent in hospital, number of medications taken and the frequency of lab procedures to be most informative of predicting readmission status. The importance of the primary diagnosis feature is that if the initial diagnosis is diabetes perhaps patients received better care during their first encounter and thus do not get readmitted [@paper].

```{r numeric_features, echo=FALSE, fig.cap="Figure 2. Distribution of Numeric Features and Readmission Status", fig.align='center', out.width = '100%'}
knitr::include_graphics("../reports/figures/figure2_numhisttarget_eda.svg")
```

Several of the categorical features were also reviewed in a similar format to the numerical features analysis, and found that metformin, insulin, and Hemoglobin A1C levels were most informative of predicting readmission status. Testing for hemoglobin levels may have resulted in applicable changes to the medications and thus better management of diabetes during their hospital stay, preventing readmission [@NI]. 

```{r categorical_features, echo=FALSE, fig.cap="Figure 3. Distribution of Categorical Features and Readmission Status", fig.align='center', out.width = '100%'}
knitr::include_graphics("../reports/figures/figure3_numcattarget_eda.svg")
```

??????)


## Discussion



## References
